---
title: "test"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Libraries
```{r}
library(tidyverse)
library(FactoMineR)
library(knitr)
```

```{r}
df <- read_csv("data/data.csv")
```

```{r}
dim(df)
names(df)
glimpse(df)
```

###change variables
```{r}
df <- df %>% rename('stream_id' = '#stream') # '#' symbol reserved for comments
df <- df %>% mutate(stream_id= factor(stream_id), isp= factor(isp), browser= factor(browser), connected= factor(connected)) #2 vars categorized
```

###Dealing with NAs
```{r}
dim(df)[1] - dim(na.omit(df))[1]

#only one NA, can be overlooked
df <- na.omit(df)
```

###EDA
```{r}
colSums(df %>% select(p2p, cdn) %>% filter(!is.na(cdn))) # total data transmitted

df %>% filter(connected==F) %>% distinct(p2p) # Observe: no backend connection <=> no p2p
```

###Visualisation of the distribution between p2p and cdn
```{r}
factors <- c(quo(stream_id), quo(isp), quo(browser), quo(connected))

for (i in seq_along(factors)) {
  temp <- df %>% group_by(!!factors[[i]]) %>% summarize(p2p= sum(p2p), cdn= sum(cdn))
  temp <- reshape2::melt(temp, id.vars= names(df)[i])
  print( ggplot(temp, aes(!!factors[[i]], value, fill = variable)) +
    geom_bar(position = "fill", stat = "identity") )
}

```



```{r}
cor.test(df$p2p, df$cdn)
```

    Statistically significant correlation between the two types of downloaded data.

###Potential Outliers    
```{r}
is_outlier <- function(x) {
  return(x < quantile(x, 0.25) - 2 * IQR(x) | x > quantile(x, 0.75) + 2 * IQR(x))
}

out_p2p <- which(is_outlier(df$p2p))
out_cdn <- which(is_outlier(df$cdn))
```

###Clustering
    
    Use k-means clustering to get fewer clusters and hierarchical clustering on top of that and decide clusters based on inertia.
    Initially, use factor analysis of mixed data to reduce noise.
    
```{r}

res.famd <- FAMD(df, ncp= Inf, graph = F)
res.famd$eig #keep 14 comp ~ 95% variance
res.famd <- FAMD(df, ncp= 14)

in_ratio <- c()
for (k in 1:30) {
  cl <- kmeans(res.famd$ind$coord, centers = k, nstart = 3)
  in_ratio <- c(in_ratio, cl$betweens/cl$totss)
}
in_ratio <- as.data.frame(in_ratio)

ggplot(in_ratio, aes(x=1:30, y=in_ratio)) + 
  geom_point(shape=1) +
  labs(title= "inertia ratio per clustering")
```


    Based on the ratio of between inertia to total inertia 9 clusters are chosen. Through catdes the clusters are described.
    
```{r}
res.kmeans <- kmeans(res.famd$ind$coord, centers = 9, nstart = 3)

cluster <- factor(res.kmeans$cluster)
df <- cbind(cluster, df)

rescatdes <- catdes(df, 1)

kable(rescatdes$category)
```


```{r}
#assign labels to clusters
lbs = c("stream_id=4", 
        "stream_id=2",
        "connected=FALSE",
        "stream_id=5",
        "stream_id=7",
        "isp=BTP",
        "stream_id=1 & stream_id=3",
        "stream_id=6",
        "browser=Vectrice")

cluster <- factor(res.kmeans$cluster, labels = lbs)

kable(cbind(levels(cluster), res.kmeans$size), col.names = c('Cluster', 'Size'))
```


###Projection of the clusters on principal components
```{r}
df_plot <- tibble(cluster, Dim_1= res.famd$ind$coord[,1], Dim_2= res.famd$ind$coord[,2])

ggplot(df_plot, aes(x= Dim_1, y= Dim_2, colour= cluster)) +
  geom_point() +
  theme_dark()
```

###data usage type per cluster
```{r}
temp <- df %>% select(cluster, p2p, cdn) %>% group_by(cluster) %>% summarize(p2p= mean(p2p), cdn= mean(cdn))

temp <- reshape2::melt(temp, id.vars= names(temp)[1])

ggplot(temp, aes(cluster, value, fill = variable)) +
    geom_bar(position = "fill", stat = "identity") 
```

